\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{The High Five: LiftLog}
\rhead{Sprint 5 Report, 3/9/2021}
\begin{document}
	\section*{Stop Doing}
		This Section is not applicable since it is the final sprint. The lessons learned were the importance of clear communication and comprehension checks. A greater structure overall and team buy in of that structure are incredibly important to the success of a project. Experience means a lot in terms of what a given team is actually capable of within a set amount of time and developers are impossible when it comes to creating a release plan as we try to mentally implement things as they are discussed, immediately jumping to the "how" and potential edge cases instead of just focusing on the "what".
	\section*{Start Doing}
		If we were to start this over from scratch I think we would have a greater focus on implementing via TDD as well as spend a little more time on investigating the technologies that we were working with in order to get a better understanding of what limitations we may face later.
	\section*{Keep Doing}
		If the project were to continue, we would focus on the continued delivery of concisely designed and user driven stories to implement more functionality into the project.
	\section*{Work Completed/Not Completed}
		As of the end of this sprint we have completed the neccesary work for our modified MVP. We had to remove tracking from the MVP due to time constraints, but we are happy with the results.
	\section*{Work Completion Rate}
		We completed 4 stories and 9 additional bugs/tasks. Please see the burnup chart in the burnup chart directory
\end{document}
