\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{The High Five: LiftLog}
\rhead{Sprint 3 Report, 2/10/2021}
\begin{document}
	\section*{Stop Doing}
		We need to stop combining many tasks into a single task, as it results in large commits that are difficult to review, and long waits to see any progress in the main branch.
	\section*{Start Doing}
		We need to start determining which stories are the most important for our MVP, as it seems that we will not be able to add all features that we want. 
It is important to ensure a high quality of work over high quantity.
	\section*{Keep Doing}
		We need to keep carefully reviewing PRs carefully, working towards a high quality product, even if it may require some more time and effort. Since we may be eliminating some features from the final sprints, we have some more time to ensure that everything else is working satisfactorily.
	\section*{Work Completed/Not Completed}
		No stories were completed in this sprint, but this was a result of working on rather substantial issues and stories that were not easily completed in one sprint.
We did manage to get our app login page with a skinned UI logging in with Firebase successfully.
	\section*{Work Completion Rate}
		1 issue was completed for this sprint. The corresponding burnup chart can be found in the burnup chart directory in this repo.
\end{document}